---
title: "Processus Stationnaire"
output:
  pdf_document: default
  html_notebook: default
---

SIMULATION DE D' UN PROCESSUS STATIONNAIRE $(X_t)_t  $ :

 i.e dont on a les conditions sont les suivantes:

1-$E(X_t) < \infty  $,  
2-$ Var(X_t) < \infty ,  $ et  
3-$ covar(Z_t, Z_k) =0  $ et $ a+b \leq 1 $ )
```{r}
```


```{r}
mu=0.25
a=0.65
b=0.25
x=c()
x[1]=0
N=1100
for  (i in 1:N){
  x[i+1]=mu + a*x[i] + b*rnorm(1)
}

x=tail(x,1000)

ts.plot(x,col="blue")
```
```{r}
X=head(x, length(x)-1)
Y=tail(x, length(x)-1)

df=data.frame(X,Y)

plot(Y~X, df)
# creation du modele lineaire

reglin=lm(Y~X)

summary(reglin)




```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
